Heuristics and A* implementations

### 2020-05-16 paper/paper.tex
Describe additive heuristic on paper

\lstinputlisting[caption={$h_{max}$ implementation}, style=pythonstyle, label=lst:h_max_python, escapechar=|]{code/h_max.py}

@@

At least, in line~\ref{line:test_unreachable:h_max_python}, it is tested whether the new reachable states are the same as the current reachable state. If true, there are no more states to reach and the heuristic has not achieved the goals. Therefore, \textit{infinite} is returned. When there are more states to test, the maximum cost is increased until all goals are reached.

@@

>>>>

\lstinputlisting[caption={$h_{max}$ implementation}, style=pythonstyle, label=lst:h_max_python, escapechar=|]{code/h_max.txt}

@@

At least, in line~\ref{line:test_unreachable:h_max_python}, it is tested whether the new reachable states are the same as the current reachable state. If true, there are no more states to reach and the heuristic has not achieved the goals. Therefore, $\inf$ is returned. When there are more states to test, the maximum cost is increased until all goals are reached.

@@

In a nutshell, this heuristic returns the sum of all the costs to reach the goals. The Listing~\ref{lst:h_add_python} shows the algorithm that performs this heuristic.

\lstinputlisting[caption={$h_{add}$ implementation}, style=pythonstyle, label=lst:h_add_python, escapechar=|]{code/h_add.txt}

Similar to the $h_{max}$ heuristic, the first reachable state will be the initial state and the cost of reaching goals that are in the initial state, is $0$ (line~\ref{line:initial_costs:h_add_python}). As we need to add the cost of reaching all goals, it is necessary to maintain a set of all goals that have not yet been achieved.

When a goal is reached in the current reachable state (line\ref{line:get_goal_reached:h_add_python}), the cost of all goals reached is added to the variable \textit{add}, as shown in line~\ref{line:reached_goal:h_add_python}.

After reaching all the goals, the variable \textit{add} is returned (line~\ref{line:return_add:h_add_python}). If some goal cannot be reached, at some point in the execution, the previous state will be equal to the reachable state, and then return $\inf$ (line~\ref{line:return_inf:h_add_python}).

The first step to get the next reachable state is to filter only the actions applicable to the current state and obtain the effects of those actions (line~\ref{line:new_reachable:h_add_python}). After that, the cost of each effect is calculated and added to the variable \textit{cost} (line~\ref{line:add_effect_cost:h_add_python}).
